Placeholder for article 3

### 2024-12-30 analysis/paper/paper.qmd
Graphs

library(readr)
library(dplyr)
library(tidyr)
library(stringr)

@@

@@

>>>>

library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)

@@

```{r}
#| label: general-tables

library(janitor)

proto_general <- phase_dataset %>% 
  filter(Level %in% c("4E", "4E/5"))
  mutate(RMTYPE = factor(RMTYPE, levels = c("TYPE 1","TYPE 2", "TYPE 3", "TYPE 4",
                                        "TYPE 5", "TYPE 6","TYPE 7", 
                                        "TYPE 8", "TYPE 9", "TYPE 10", "TYPE 11", "TL", "INDET"))) %>%
  tabyl(RMTYPE, CLASS) %>%
  adorn_totals(c("row", "col")) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(2) %>%
  adorn_ns("front")

proto_graph <- proto_general %>% 
  dplyr::group_by(RMTYPE, CLASS) %>%
  dplyr::summarise(n = n())
  #mutate(percent = n/sum(n))

proto_graph <- ggplot(proto_graph, aes(x=RMTYPE,y=n, fill = CLASS)) +
  geom_bar(stat = "identity", width = 0.5) +
  #scale_y_continuous(labels = scales::percent_format()) +
  #theme_minimal() + #type of theme
  labs(y = "Count %") +# change labels
  guides(fill=guide_legend(title=NULL)) + # remove legend title
  geom_text() +
  #geom_text(aes(label=ifelse(percent >= 0.05, paste0(sprintf("%.1f", percent*100),"%"),"")),
  #          position=position_stack(vjust=0.5), colour="white", size=3) +
  theme(axis.title.x = element_blank()) +
  scale_fill_manual(values = c("#C74B50", "#D49B54", "#911F27", "#630A10",
                               "#FACE7F", "#845460", "#EAD3CB", "#BDC7C9",
                               "#2B4F60", "#BDD2B6", "#798777", "#FCF0C8"))

@@

```{r}
#| label: stats

proto_stats_blanks <- phase_dataset %>% 
  filter(Level %in% c("4E", "4E/5")) %>% 
  filter(RMTYPE != "INDET") %>% 
  mutate(CLASS = case_when(
    CLASS == "BlankFrag" & PIECECOMPLETENESS == "Proximal" ~ "BlankFragProx", # To add proximal fragments to ratio
    TRUE ~ CLASS)) %>% 
  filter(CLASS %in% c("Blank", "Core", "BlankFragProx", "RetouchedPiece")) %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))

proto_stats_blanks <- phase_dataset %>% 
  filter(Level %in% c("4E", "4E/5")) %>% 
  filter(RMTYPE != "INDET") %>% 
  mutate(CLASS = case_when(
    CLASS == "BlankFrag" & PIECECOMPLETENESS == "Proximal" ~ "BlankFragProx", # To add proximal fragments to ratio
    TRUE ~ CLASS)) %>% 
  filter(CLASS %in% c("Blank", "Core", "BlankFragProx", "RetouchedPiece")) %>%
  select(RMTYPE, CLASS, THICKNESS, MAXWIDTH, LENGTH, WEIGHT) %>% 
  group_by(RMTYPE, CLASS) %>% 
  summarise(across(c(THICKNESS, MAXWIDTH, LENGTH, WEIGHT), list(mean = mean, sd = sd, max = max, min = min)))
